Cell Decompositions for Rank Two Quiver Grassmannians

### 2017-11-17 Grassmannian_cells.tex
Reorganization

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Terminology and Preliminary results}

Incorporate these into other sections...

\subsection{Covering theory}\footnote{more and more precise definitions}
For an introduction to covering theory we refer to \cite{gab}. Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$. We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$. Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.  
\begin{definition}
The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.

\section{Torus Actions on Quiver Grassmannians}\label{torusaction}

Define quiver representations and quiver Grassmannians...

\section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
\noindent 
Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$. Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique. On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$. In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_l)$ with $j_i\leq n$ and $l\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $1\leq k\leq n-1$, there exist exact sequences of the form
\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.

Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
\section{Combinatorial description of non-empty cells}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Terminology and Preliminary results}

Incorporate this into other sections...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Torus Actions on Quiver Grassmannians}
\label{torusaction}

Move this somewhere...

For an introduction to covering theory we refer to \cite{gab}. Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$. We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$. Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.  
\begin{definition}
The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.

\section{Representation Theory of $K(n)$}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
\noindent 
Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$. Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique. On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$. In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_l)$ with $j_i\leq n$ and $l\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $1\leq k\leq n-1$, there exist exact sequences of the form
\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combinatorial description of non-empty cells}

@@

\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.

Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
